---
title: "Working with FARS Data"
author: "Matt Adams"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Working with FARS Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This package allows for easy operation on data from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System, which is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes.

# Example Workflow

As an example, we will outline a potential analysis with FARS data.

### Getting the data

```{r, message=FALSE}
# devtools::install_github("madams1/courserapackage")
require(courserapackage)
require(dplyr)
require(readr)

fars_2015_file <- system.file("extdata", make_filename(2015), package = "courserapackage")
fars_path <- dirname(fars_2015_file)
fars_2015_data <- fars_read(fars_2015_file)
```

We can see what this data looks like:

```{r}
fars_2015_data
```

### Summarize multiple years

```{r}
fars_summarize_years(2013:2015, path = fars_path)
```


### Make a map for a U.S. state

Plot accidents on a map of California that occurred in 2015.

```{r, fig.show='hold', message=FALSE}
require(maps)
fars_map_state(6, 2015, path = fars_path)
```

